\documentclass[main]{subfiles}
%\setcounter{section}{-1}
\begin{document}
\section*{Organisation}
The content is organised similarly to the Fall 2021 course schedule, thought it is not exactly the same. 
We chose to separate lecture 2 and 3 into two distinct chapters: Transistor Physics and Transistor Operation. This structure, similar to the Textbook, felt more natural and clearer. We also grouped both Photosensor and Photoreceptor lectures. The chapters are best read in order, as much of the content from a given chapter builds on the content from previous chapters. 
Each chapter contains the following: 
\begin{itemize}
  \item Short introduction about the objectives of the lecture, and some contextualization of the topic into the field of Neuromorphic Engineering and beyond. 
  \item List of all topics previously covered that should be understood in order to properly digest the content of the chapter.
  \item Content of the chapter, organized, to the best of our capability, in a logical manner (sometimes not exactly matching the lecture structure).
  \item Lab Summary and takeaways.
  \item List of all concepts to know for the exam. These are often (though not exclusively) taken from the "Study Winter Sheet"\footnote{This is a revision sheet available on OLAT that should guide revision. However, one should note that many topics mentioned in this study sheet were not covered during Fall 2021, and that several important things that we believe should be known are not mentioned in the sheet. We also included it in the Appendix for reference.}.
  
\end{itemize}
Additionally, we added the following extra chapters for reference: 
\begin{itemize}
    \item Chapter 0: Stupid-Proof explanations of fundamental Electrical Engineering / Physics / Neuroscience for the uninitiated. Warning: This chapter may contain approximations and inaccuracies. 
    \item Circuit recap - a revision sheet for the most important circuits, their function, equations and diagram.
    \item Advice for exam preparation.
    \item Important constants (It is being said that Tobi likes to ask about these in the exam!) 
\end{itemize}
\end{document}